Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
added wreckage figure, made intro page break, added louis, gregg peters to acknowledgments, dropped chris from advisors because we dont know his last name

We are advised by
 Professor Tobias Rossmann,
 and several members of the Tri-County R/C Club \cite{tricountyRC}:
 Larry Kosinar,
 Bill Perkowski,
 Mike Korb,
 (the man who donated daedalus), and
 Chris (test pilot) amongst many who spent time mentoring us.

@@

We would like to acknowledge
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg (last name) of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

\section{Systems Engineering}

\subsection{Goals}
For this entry, we took a close look at our goals and requirements, and dialed back our approach to ensure we would meet the most basic competition requirements successfully.
We started the design by forming, as a team, some broad goals based on our experience in the 2009 competition.
These formed the basis on which sub-teams and individuals tackled the smaller problems while still keeping an eye on the big picture.

>>>>

We are advised by
 Professor Tobias Rossmann,
 and several members of the Tri-County R/C Club \cite{tricountyRC}:
 Larry Kosinar,
 Bill Perkowski,
and  Mike Korb, 
%and Chris (test pilot) 
amongst many who spent time mentoring us.

@@

We would like to acknowledge
Louis Stumpf, for donating the aircraft which became the \emph{Daedalus};
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg Peters of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black;
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

\begin{figure}[b]
	\centering
	\includegraphics[width=0.6\textwidth]{../images/wreckage.jpg}
	\caption{The recovery of our 2009 entry, the \emph{Icarus}}
	\label{fig:wreckage}
\end{figure}

\newpage
\section{Systems Engineering}
\subsection{Goals}
For this entry, we took a close look at our goals and requirements, and dialed back our approach to ensure we would meet the most basic competition requirements successfully.
We started the design by forming, as a team, some broad goals based on our experience in the 2009 competition.
These formed the basis on which sub-teams and individuals tackled the smaller problems while still keeping an eye on the big picture.
